Contracts for Contracts

### 2023-07-11 paper/introduction.tex
add DAO citation

Undoubtedly, the past few years have witnessed several catastrophic failures
of blockchain systems resulting from attacks on vulnerable contract programs.
One prominent instance is the well-known DAO hack \note{cite} where an unauthorized
attacker exploited the recursive function calls and callback mechanism, leading
to a staggering loss of \textdollar50 million. The fundamental issue at the core of this
attack was the failure of the deployed contract to prevent reentrancy under
critical conditions.

>>>>

Undoubtedly, the past few years have witnessed several catastrophic failures
of blockchain systems resulting from attacks on vulnerable contract programs.
One prominent instance is the well-known DAO hack~\cite{DAOhack} where an unauthorized
attacker exploited the recursive function calls and callback mechanism, leading
to a staggering loss of \textdollar50 million. The fundamental issue at the core of this
attack was the failure of the deployed contract to prevent reentrancy under
critical conditions.
